### 2015-02-08 Doc/ms.Rmd
set up project

% Relationships between environmental variabels and species richness
% D. Li \and D. Waller
% Working paper -- \today

**Running headline**: Environment and species richness

**Abstract**: Your awesome abstract here.

\clearpage

### 2015-02-08 Doc/ms.tex
set up project

%!TEX TS-program = pdflatex
\documentclass[12pt]{article} %article

% The declaration of the document class:
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

\usepackage[full]{textcomp}
\usepackage[T1]{fontenc}
%\usepackage{kpfonts}
\usepackage[utf8]{inputenc}
\usepackage{lineno}

\usepackage{pgfplots,pgfplotstable}
\usepackage{longtable}
\usepackage{booktabs}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\pagestyle{plain}
\usepackage{setspace}

% Table formatting:
% What if you make a table? -- Pandoc knows, of course, and
% then declares that its variable `table` is True and
% imports a table package suitable to its pleasantly simple tables.
% Needless to say infinitely complicated tables are possible in
% LaTeX with suitable packages. We are spared the temptation:

\usepackage{array}

% Continuing on the topic of tables ... (we havent reached `endif`).
% The commented out line below is in the default pandoc latex.template.
% Some unpleasantness with table formatting must be corrected.

% -- This is needed because raggedright in table elements redefines \\:
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

% Subscripts:
% Pandoc remembers whether you used subscripts, assigning True to
% its `subscript` variable
% It then needs to adopt a default with an incantation like this:

% Web-style links:

% markdown inclines us to use links, since our texts can be made into html.
% Why not have clickable blue links even in
% learned, scientific, religious, juridical, poetical and other suchlike texts?
% Never mind that they have been proven to destroy the nervous system!

% First, what about the fact that links like http://example.com are
% technically code and thus must not be broken across lines?
% [breaklinks=true] to the rescue!

% Nowadays LaTeX can handle all of this with another half million macros:

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
	citecolor=blue,%
	filecolor=blue,%
	linkcolor=blue,%
	urlcolor=blue}

% Images.
% In ye olde LaTeX one could only import a limited range of image
% types, e.g. the forgotten .eps files. Or else one simply drew the image
% with suitable
% commands and drawing packages. Today we want to import .jpg files we make
% with
% our smart phones or whatever:

\usepackage{graphicx}
% -- We will generate all images so they have a width \maxwidth. This means
% -- that they will get their normal width if they fit onto the page, but
% -- are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
	\else\Gin@nat@width\fi}
	\makeatother
	\let\Oldincludegraphics\includegraphics
	\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

% Section numbering.
% Here again is a variable you can specify on the commandline
% `markdown2pdf my.txt --number-sections --xetex
% --template=/wherever/this/is -o my.pdf`

% Footnotes:
% Wait, didn't we already discuss the crisis of code in footnotes?
% Evidently the order of unfolding of macros required that
% we import a package to deal with them earlier
% and issue a command it defines now. (Or maybe that's not the reason;
	% very often the order does matter as the insane system of macro
	% expansion
	% must take place by stages.)

% Other stuff you specify on the command line:
% You can include stuff for the header from a file specified on the
% command line;
% I've never done this, but that stuff will go here:

% Title, authors, date.
% If you specified title authors and date at the start of
% your pandoc-markdown file, pandoc knows the 'values' of the
% variables: title authors date and fills them in.

\title{Relationships between environmental variabels and species richness}
\author{D. Li \and D. Waller}
\date{Working paper -- \today}

% At last:
% The document itself!:

% After filling in all these blanks above, or erasing them
% where they are not needed, Pandoc has finished writing the
% famous LaTeX *preamble* for your document.
% Now comes the all-important command \begin{document}
% which as you can see, will be paired with an \end{document} at the end.
% Pandoc knows whether you have a title, and has already
% specified what it is; if so, it demands that the title be rendered.
% Pandoc knows whether you want a table of contents, you
% specify this on the command line.
% Then, after fiddling with alignments, there comes the real
% business: pandoc slaps its rendering of your text in the place of
% the variable `body`
% It then concludes the document it has been writing.

% \setpagewiselinenumbers
\linenumbers

\begin{document}

\maketitle

\doublespacing
\textbf{Running headline}: Environment and species richness

\textbf{Abstract}: Your awesome abstract here.

\clearpage

\section{Introduction}\label{introduction}

Here is your introduction. It should describe clearly the rationale for
the study being done and the previous work related with the study. It
should also tell readers about your specific hypothese/questions being
addressed. Citations will be like this (Adair et al. 2010), or (e.g.,
Clark and Tilman 2008), or (Eriksson and Ehrlén 1993, Williamson et al.
1999)

\section{Methods}\label{methods}

Here is the method section. You can include equations easily. For inline
equations, use \(\text{var}(X) = p(1-p)\). For display equation, use

\begin{equation}
\text{var}(X) = p(1-p)
\end{equation}

\subsection{Results}\label{results}

Insert tables:

\begin{longtable}[c]{@{}rr@{}}
\toprule
Plot & sprich\tabularnewline
\midrule
\endhead
3294 & 31\tabularnewline
3297 & 28\tabularnewline
3299 & 26\tabularnewline
3330 & 27\tabularnewline
\bottomrule
\end{longtable}

Or put results inline, e.g.~the mean species richness is 28.

How about figures? We illustrate this in Fig. \ref{f:plot}.

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{Figs/plot.pdf}
\caption{Caption here.\label{f:plot}}
\end{figure}

\clearpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

Adair, E. C. et al. 2010. Single-pool exponential decomposition models:
Potential pitfalls in their use in ecological studies. - Ecology 91:
1225--1236.

Clark, C. M. and Tilman, D. 2008. Loss of plant species after chronic
low-level nitrogen deposition to prairie grasslands. - Nature 451:
712--715.

Eriksson, O. and Ehrlén, J. 1993. Seed and microsite limitation of
recruitment in plant populations. - Oecologia 92: 361--366.

Williamson, C. E. et al. 1999. Dissolved organic carbon and nutrients as
regulators of lake ecosystems: Resurrection of a more integrated
paradigm. - Limnology and Oceanography 44: 795--803.

%

\end{document}

### 2015-02-08 R/rcode.R

@@ -1,0 +1,46 @@
+# packages needed
+library(stringr)
+library(plyr)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+# read data into R
+under2012=read.csv("Data/Raw_data/under2012.csv",stringsAsFactors=F)
+envi = read.csv("Data/Raw_data/envi.csv")
+
+# data clean: you should clean your data with scripts instead of doing it 
+# in Excel. By using scripts, you recorded all of your history about data 
+# clean. You should also make comments about why you changed your data.
+# names(under2012)
+under2012$Genera=str_trim(under2012$Genera) #remove spaces before and after sp.names.
+under2012$species=str_trim(under2012$species) 
+under2012[under2012$species=="sp",]$species="spp" # change sp to spp
+under2012$sp=paste(under2012$Genera,under2012$species) # combine genus and sp
+# sort(unique(under2012$sp))
+
+## correct sp names' typo and errors
+under2012[under2012$sp=="Accer rubrum",]$sp="Acer rubrum"
+under2012[under2012$sp=="Acrtostaphylos uva-ursi",]$sp="Arctostaphylos uva-ursi"
+under2012[under2012$sp=="Carex pennsylvanica",]$sp="Carex pensylvanica"
+
+# remove columns we do not need
+under2012 = under2012[c("Plot", "Transect", "Quadrat", "sp", "Count")]
+under2012$Count[is.na(under2012$Count)] = 1 # replace NA with 1.
+
+## analysis ---------------------
+
+# how many sp each site has?
+sprich = ddply(under2012, .(Plot), summarize, sprich = length(unique(sp)))
+meansprich = mean(sprich$sprich)
+
+# relationship between sprich and envi?
+envi.long = gather(data = envi, key = envi, value = value, -Plot) 
+    # wide table to long table
+envi.sprich = merge(envi.long, sprich, by = "Plot")
+
+# plot it
+pl = ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
+  geom_point() + geom_smooth(method = "lm") +
+  facet_wrap(~envi, scales = "free_x") + theme_bw()
+ggsave(filename = "Figs/plot.pdf", pl, width = 6, height = 6, units = "in")

### 2015-02-08 Doc/ms.Rmd
introduction of ms

@@
 \clearpage
+
+# Introduction
+
+Here is your introduction.
+It should describe clearly the rationale for the study being done and the previous work related with the study.
+It should also tell readers about your specific hypothese/questions being addressed.
+Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993;@williamson_dissolved_1999]

### 2015-02-08 Doc/ms.Rmd
methods of ms
results and references of ms

@@
 Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993;@williamson_dissolved_1999]
+
+# Methods
+
+Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use
+
+\begin{equation}
+\text{var}(X) = p(1-p)
+\end{equation}
+
+## Results
+
+Insert tables:
+
+```{r table,results='asis',echo=FALSE}
+load("../R/.RData")
+library(knitr)
+kable(sprich)
+```
+
+Or put results inline, e.g. the mean species richness is `r meansprich`.
+
+<!-- 
+Or you can type tables by hand:
+
+Col A             Col B       Col C                   Col D
+------------      -------     ------------------      ------------------
+row 1             190         $112 \pm 2$             $233 \pm 3$
+$\eta$            0.13        0.12                    0.12
+$\eta^2$          0.14        0.13                    0.50
+$\eta^3$          0.15        0.31                    0.52
+
+Using `xtable` package in R:
+
+```{r echo=F,results='asis',warning=F,message=F}
+library(xtable)
+data(tli)
+## Demonstrate aov
+ ## Taken from help(aov) in R 1.1.1
+ ## From Venables and Ripley (1997) p.210.
+ N <- c(0,1,0,1,1,1,0,0,0,1,1,0,1,1,0,0,1,0,1,0,1,1,0,0)
+ P <- c(1,1,0,0,0,1,0,1,1,1,0,0,0,1,0,1,1,0,0,1,0,1,1,0)
+ K <- c(1,0,0,1,0,1,1,0,0,1,0,1,0,1,1,0,0,0,1,1,1,0,1,0)
+ yield <- c(49.5,62.8,46.8,57.0,59.8,58.5,55.5,56.0,62.8,55.8,69.5,55.0,
++            62.0,48.8,45.5,44.2,52.0,51.5,49.8,48.8,57.2,59.0,53.2,56.0)
+ npk <- data.frame(block=gl(6,4), N=factor(N), P=factor(P), K=factor(K), yield=yield)
+ npk.aov <- aov(yield ~ block + N*P*K, npk)
+ op <- options(contrasts=c("contr.helmert", "contr.treatment"))
+ npk.aovE <- aov(yield ~  N*P*K + Error(block), npk)
+ options(op)
+
+ xsum <- xtable(summary(npk.aov))
+print(xsum,
+      floating=F,
+      hline.after=NULL,
+      add.to.row=list(pos=list(-1,0, nrow(xsum)),
+      command=c(
+           '\\toprule\n',
+          '\\midrule\n',
+           '\\bottomrule\n')))
+```
+ -->
+
+How about figures? We illustrate this in Fig. \ref{f:plot}.
+
+\clearpage
+
+[f:plot]: Figs/plot.pdf
+![Caption here.\label{f:plot}][f:plot]
+
+\clearpage
+
+# References

### 2015-02-10 Doc/ms.Rmd
update with examples about table cross-ref

--- 2015-02-08 Doc/ms.Rmd
@@
 Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993;@williamson_dissolved_1999]
+
+Here is the second paragraph of the introduction.
+
+# Methods
+
+Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use
+
+\begin{equation}
+\text{var}(X) = p(1-p)
+\end{equation}
+
+## Results
+
+#### Insert tables by `kable` in knitr package in R
+
+```{r table,results='asis',echo=FALSE,message=F,warning=F}
+# load("../R/.RData")
+source("../R/rcode.R")
+library(knitr)
+kable(sprich)
+```
+
+Put results inline, e.g. the mean species richness is `r meansprich`.
+
+#### Insert tables by `xtable` package in R
+
+Show as Table. \ref{t:anova}:
+
+```{r echo=F,results='asis',warning=F,message=F}
+library(xtable)
+envi.summ = xtable(summary(envi.aov),label = "t:anova", caption = "Caption here")
+print(envi.summ,
+		caption.placement = "top",
+	  floating=T,
+	  hline.after=NULL,
+	  comment = FALSE,
+	  add.to.row=list(pos=list(-1,0, nrow(envi.summ)),
+	  command=c(
+		   '\\toprule\n',
+		  '\\midrule\n',
+		   '\\bottomrule\n')))
+```
+
+#### Insert tables by hand
+
+Show as Table. \ref{t:byhand}:
+
+Table: Caption here. \label{t:byhand}
+
+Col A             Col B       Col C                   Col D
+------------      -------     ------------------      ------------------
+row 1             190         $112 \pm 2$             $233 \pm 3$
+$\eta$            0.13        0.12                    0.12
+$\eta^2$          0.14        0.13                    0.50
+$\eta^3$          0.15        0.31                    0.52
+
+#### Figures
+
+How about figures? We illustrate this in Fig. \ref{f:plot}.
+
+\clearpage
+
+[f:plot]: Figs/plot.pdf
+![Caption here.\label{f:plot}][f:plot]
+
+\clearpage
+
+# References

### 2015-02-10 R/rcode.R

@@ -6,8 +6,8 @@ library(tidyr)
 library(ggplot2)
 
 # read data into R
-under2012=read.csv("Data/Raw_data/under2012.csv",stringsAsFactors=F)
-envi = read.csv("Data/Raw_data/envi.csv")
+under2012=read.csv("../Data/Raw_data/under2012.csv",stringsAsFactors=F)
+envi = read.csv("../Data/Raw_data/envi.csv")
 
 # data clean: you should clean your data with scripts instead of doing it 
 # in Excel. By using scripts, you recorded all of your history about data 
@@ -39,8 +39,10 @@ envi.long = gather(data = envi, key = envi, value = value, -Plot)
     # wide table to long table
 envi.sprich = merge(envi.long, sprich, by = "Plot")
 
+envi.aov = aov(sprich ~ pH + shade, data = merge(envi, sprich, by = "Plot"))
+
 # plot it
 pl = ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
   geom_point() + geom_smooth(method = "lm") +
   facet_wrap(~envi, scales = "free_x") + theme_bw()
-ggsave(filename = "Figs/plot.pdf", pl, width = 6, height = 6, units = "in")
+ggsave(filename = "../Figs/plot.pdf", pl, width = 6, height = 6, units = "in")

### 2017-02-28 Doc/ms.Rmd
update with bookdown package

@@
-% Relationships between environmental variabels and species richness
-% D. Li \and D. Waller
-% Working paper -- \today
+---
+title: "Your Awesome Title"
+author: "Author One and Author Two"
+date: '`r format(Sys.time())`'
+output:
+  bookdown::pdf_document2:
+    includes:
+      before_body: doc_prefix.tex
+      in_header: preamble.tex
+    keep_tex: yes
+    latex_engine: xelatex
+    number_sections: no
+    toc: no
+  bookdown::html_document2:
+    number_sections: no
+    theme: readable
+    toc: yes
+  bookdown::tufte_html2:
+    number_sections: no
+    toc: yes
+  bookdown::word_document2: null
+fontsize: 12pt
+link-citations: yes
+csl: oikos.csl
+bibliography: ref.bib
+---
+
+```{r knitr_options, echo=FALSE}
+library(knitr)
+# rstudio will set the folder where .Rmd file seats as work directory
+# set it back to the folder where .Rproj seats
+opts_knit$set(root.dir = normalizePath("../")) 
+opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
+options(digits = 3, width = 88)
+```
 
@@
 It should also tell readers about your specific hypothese/questions being addressed.
-Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993;@williamson_dissolved_1999]
+Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993; @williamson_dissolved_1999]
 
@@
 
-\begin{equation}
-\text{var}(X) = p(1-p)
-\end{equation}
+$$\text{var}(X) = p(1-p)$$
 
@@
 
-#### Insert tables by `kable` in knitr package in R
+#### Tables
 
-```{r table,results='asis',echo=FALSE,message=F,warning=F}
-# load("../R/.RData")
-source("../R/rcode.R")
-library(knitr)
-kable(sprich)
+Insert tables by `kable` in knitr package in R. Then cross-reference it back with: see Table \@ref(tab:tableName).
+
+```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
+source("R/rcode.R")
+knitr::kable(sprich, booktabs = T, caption = "Caption here.")
 ```
@@
 
-Show as Table. \ref{t:byhand}:
+Show as Table. \@ref(tab:byhand):
 
-Table: Caption here. \label{t:byhand}
+Table: (#tab:byhand) Caption here.
 
@@
 
-How about figures? We illustrate this in Fig. \ref{f:plot}.
+Insert figure by code chunk. And cross-ref it back as Figure \@ref(fig:figName).
 
-\clearpage
+```{r figName, fig.width=7, fig.asp=1, fig.cap="Your caption here."}
+ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
+  geom_point() + geom_smooth(method = "lm") +
+  facet_wrap(~envi, scales = "free_x") + theme_bw()
+```
 
-[f:plot]: Figs/plot.pdf
-![Caption here.\label{f:plot}][f:plot]
+Or if you already have the figure: 
+And cite it as Figure \@ref(fig:fig2).
+
+```{r fig2, out.width='70%', fig.cap="Caption here."}
+knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
+```
 

### 2017-02-28 Doc/ms.tex
update with bookdown package

@@
-%!TEX TS-program = pdflatex
-\documentclass[12pt]{article} %article
+\documentclass[12pt,]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Your Awesome Title},
+            pdfauthor={Author One and Author Two},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-% The declaration of the document class:
-\usepackage{amsmath}
-\usepackage[english]{babel}
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+  \title{Your Awesome Title}
+  \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+  \author{Author One and Author Two}
+  \preauthor{\centering\large\emph}
+  \postauthor{\par}
+  \predate{\centering\large\emph}
+  \postdate{\par}
+  \date{2017-02-28 12:56:45}
+
 \usepackage{geometry}
@@
 
-\usepackage[full]{textcomp}
-\usepackage[T1]{fontenc}
-%\usepackage{kpfonts}
+% \usepackage[breaklinks=true,pdfstartview=FitH,citecolor=blue]{hyperref}
+\hypersetup{colorlinks,%
+	citecolor=blue,%
+	filecolor=red,%
+	linkcolor=blue,%
+	urlcolor=red,%
+	pdfstartview=FitH}
+
 \usepackage[utf8]{inputenc}
-\usepackage{lineno}
 
-\usepackage{pgfplots,pgfplotstable}
-\usepackage{longtable}
 \usepackage{booktabs}
 
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
+\usepackage{setspace}
+\doublespacing
 
-\pagestyle{plain}
-\usepackage{setspace}
+% \setstretch{1.8999999999999999}
 
-% Table formatting:
-% What if you make a table? -- Pandoc knows, of course, and
-% then declares that its variable `table` is True and
-% imports a table package suitable to its pleasantly simple tables.
-% Needless to say infinitely complicated tables are possible in
-% LaTeX with suitable packages. We are spared the temptation:
-
-\usepackage{array}
-
-% Continuing on the topic of tables ... (we havent reached `endif`).
-% The commented out line below is in the default pandoc latex.template.
-% Some unpleasantness with table formatting must be corrected.
-
-% -- This is needed because raggedright in table elements redefines \\:
-\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
-\let\PBS=\PreserveBackslash
-
-% Subscripts:
-% Pandoc remembers whether you used subscripts, assigning True to
-% its `subscript` variable
-% It then needs to adopt a default with an incantation like this:
-
-% Web-style links:
-
-% markdown inclines us to use links, since our texts can be made into html.
-% Why not have clickable blue links even in
-% learned, scientific, religious, juridical, poetical and other suchlike texts?
-% Never mind that they have been proven to destroy the nervous system!
-
-% First, what about the fact that links like http://example.com are
-% technically code and thus must not be broken across lines?
-% [breaklinks=true] to the rescue!
-
-% Nowadays LaTeX can handle all of this with another half million macros:
-
-\usepackage[breaklinks=true]{hyperref}
-\hypersetup{colorlinks,%
-	citecolor=blue,%
-	filecolor=blue,%
-	linkcolor=blue,%
-	urlcolor=blue}
-
-% Images.
-% In ye olde LaTeX one could only import a limited range of image
-% types, e.g. the forgotten .eps files. Or else one simply drew the image
-% with suitable
-% commands and drawing packages. Today we want to import .jpg files we make
-% with
-% our smart phones or whatever:
-
-\usepackage{graphicx}
-% -- We will generate all images so they have a width \maxwidth. This means
-% -- that they will get their normal width if they fit onto the page, but
-% -- are scaled down if they would overflow the margins.
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
-	\else\Gin@nat@width\fi}
-	\makeatother
-	\let\Oldincludegraphics\includegraphics
-	\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
-
-% Section numbering.
-% Here again is a variable you can specify on the commandline
-% `markdown2pdf my.txt --number-sections --xetex
-% --template=/wherever/this/is -o my.pdf`
-
-% Footnotes:
-% Wait, didn't we already discuss the crisis of code in footnotes?
-% Evidently the order of unfolding of macros required that
-% we import a package to deal with them earlier
-% and issue a command it defines now. (Or maybe that's not the reason;
-	% very often the order does matter as the insane system of macro
-	% expansion
-	% must take place by stages.)
-
-% Other stuff you specify on the command line:
-% You can include stuff for the header from a file specified on the
-% command line;
-% I've never done this, but that stuff will go here:
-
-% Title, authors, date.
-% If you specified title authors and date at the start of
-% your pandoc-markdown file, pandoc knows the 'values' of the
-% variables: title authors date and fills them in.
-
-\title{Relationships between environmental variabels and species richness}
-\author{D. Li \and D. Waller}
-\date{Working paper -- \today}
-
-% At last:
-% The document itself!:
-
-% After filling in all these blanks above, or erasing them
-% where they are not needed, Pandoc has finished writing the
-% famous LaTeX *preamble* for your document.
-% Now comes the all-important command \begin{document}
-% which as you can see, will be paired with an \end{document} at the end.
-% Pandoc knows whether you have a title, and has already
-% specified what it is; if so, it demands that the title be rendered.
-% Pandoc knows whether you want a table of contents, you
-% specify this on the command line.
-% Then, after fiddling with alignments, there comes the real
-% business: pandoc slaps its rendering of your text in the place of
-% the variable `body`
-% It then concludes the document it has been writing.
-
-% \setpagewiselinenumbers
+\usepackage{lineno}
 \linenumbers
 
+\renewcommand{\rmdefault}{cmr}
+
+% flush left while keep identation
+\makeatletter
+\newcommand\iraggedright{%
+  \let\\\@centercr\@rightskip\@flushglue \rightskip\@rightskip
+  \leftskip\z@skip}
+\makeatother
+
 \begin{document}
-
 \maketitle
 
-\doublespacing
+% align only at left, not at right.
+\iraggedright
+
 \textbf{Running headline}: Environment and species richness
@@
 should also tell readers about your specific hypothese/questions being
-addressed. Citations will be like this (Adair et al. 2010), or (e.g.,
-Clark and Tilman 2008), or (Eriksson and Ehrlén 1993, Williamson et al.
-1999)
+addressed. Citations will be like this (Adair et al.
+\protect\hyperlink{ref-adair_single-pool_2010}{2010}), or (e.g., Clark
+and Tilman \protect\hyperlink{ref-clark_loss_2008}{2008}), or (Eriksson
+and Ehrlén \protect\hyperlink{ref-eriksson_seed_1993}{1993}, Williamson
+et al. \protect\hyperlink{ref-williamson_dissolved_1999}{1999})
+
+Here is the second paragraph of the introduction.
 
@@
 
-\begin{equation}
-\text{var}(X) = p(1-p)
-\end{equation}
+\[\text{var}(X) = p(1-p)\]
 
@@
 
-Insert tables:
+\paragraph{Tables}\label{tables}
 
-\begin{longtable}[c]{@{}rr@{}}
+Insert tables by \texttt{kable} in knitr package in R. Then
+cross-reference it back with: see Table \ref{tab:tableName}.
+
+\begin{table}
+
+\caption{\label{tab:tableName}Caption here.}
+\centering
+\begin{tabular}[t]{rr}
 \toprule
-Plot & sprich\tabularnewline
+Plot & sprich\\
+\midrule
+3294 & 31\\
+3297 & 28\\
+3299 & 26\\
+3330 & 27\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Put results inline, e.g.~the mean species richness is 28.
+
+\paragraph{\texorpdfstring{Insert tables by \texttt{xtable} package in
+R}{Insert tables by xtable package in R}}\label{insert-tables-by-xtable-package-in-r}
+
+Show as Table. \ref{t:anova}:
+
+\begin{table}[ht]
+\centering
+\caption{Caption here} 
+\label{t:anova}
+\begin{tabular}{lrrrrr}
+  \toprule
+ & Df & Sum Sq & Mean Sq & F value & Pr($>$F) \\ 
+  \midrule
+pH          & 1 & 4.58 & 4.58 & 4.77 & 0.2733 \\ 
+  shade       & 1 & 8.45 & 8.45 & 8.80 & 0.2070 \\ 
+  Residuals   & 1 & 0.96 & 0.96 &  &  \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
+
+\paragraph{Insert tables by hand}\label{insert-tables-by-hand}
+
+Show as Table. \ref{tab:byhand}:
+
+\begin{longtable}[]{@{}llll@{}}
+\caption{\label{tab:byhand} Caption here.}\tabularnewline
+\toprule
+Col A & Col B & Col C & Col D\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Col A & Col B & Col C & Col D\tabularnewline
 \midrule
 \endhead
-3294 & 31\tabularnewline
-3297 & 28\tabularnewline
-3299 & 26\tabularnewline
-3330 & 27\tabularnewline
+row 1 & 190 & \(112 \pm 2\) & \(233 \pm 3\)\tabularnewline
+\(\eta\) & 0.13 & 0.12 & 0.12\tabularnewline
+\(\eta^2\) & 0.14 & 0.13 & 0.50\tabularnewline
+\(\eta^3\) & 0.15 & 0.31 & 0.52\tabularnewline
 \bottomrule
@@
 
-Or put results inline, e.g.~the mean species richness is 28.
+\paragraph{Figures}\label{figures}
 
-How about figures? We illustrate this in Fig. \ref{f:plot}.
+Insert figure by code chunk. And cross-ref it back as Figure
+\ref{fig:figName}.
 
-\clearpage
+\begin{figure}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{Figs/plot.pdf}
-\caption{Caption here.\label{f:plot}}
+{\centering \includegraphics{ms_files/figure-latex/figName-1}
+
+}
+
+\caption{Your caption here.}\label{fig:figName}
+\end{figure}
+
+Or if you already have the figure: And cite it as Figure \ref{fig:fig2}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{/Users/dli/Github/workflow_demo/Figs/plot}
+
+}
+
+\caption{Caption here.}\label{fig:fig2}
 \end{figure}
@@
 
+\hypertarget{refs}{}
+\hypertarget{ref-adair_single-pool_2010}{}
 Adair, E. C. et al. 2010. Single-pool exponential decomposition models:
@@
 
+\hypertarget{ref-clark_loss_2008}{}
 Clark, C. M. and Tilman, D. 2008. Loss of plant species after chronic
@@
 
+\hypertarget{ref-eriksson_seed_1993}{}
 Eriksson, O. and Ehrlén, J. 1993. Seed and microsite limitation of
@@
 
+\hypertarget{ref-williamson_dissolved_1999}{}
 Williamson, C. E. et al. 1999. Dissolved organic carbon and nutrients as
@@
 
-%
-
 \end{document}

### 2017-02-28 R/rcode.R

@@ -6,8 +6,8 @@ library(tidyr)
 library(ggplot2)
 
 # read data into R
-under2012=read.csv("../Data/Raw_data/under2012.csv",stringsAsFactors=F)
-envi = read.csv("../Data/Raw_data/envi.csv")
+under2012=read.csv("Data/Raw_data/under2012.csv",stringsAsFactors=F)
+envi = read.csv("Data/Raw_data/envi.csv")
 
 # data clean: you should clean your data with scripts instead of doing it 
 # in Excel. By using scripts, you recorded all of your history about data 
@@ -45,4 +45,4 @@ envi.aov = aov(sprich ~ pH + shade, data = merge(envi, sprich, by = "Plot"))
 pl = ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
   geom_point() + geom_smooth(method = "lm") +
   facet_wrap(~envi, scales = "free_x") + theme_bw()
-ggsave(filename = "../Figs/plot.pdf", pl, width = 6, height = 6, units = "in")
+ggsave(filename = "Figs/plot.pdf", pl, width = 6, height = 6, units = "in")

### 2017-04-26 Doc/ms.Rmd
bookdown url
relocate template files

@@
     includes:
-      before_body: doc_prefix.tex
-      in_header: preamble.tex
+      before_body: ../template/doc_prefix.tex
+      in_header: ../template/preamble.tex
     keep_tex: yes
-    latex_engine: xelatex
+    latex_engine: pdflatex
     number_sections: no
@@
 link-citations: yes
-csl: oikos.csl
-bibliography: ref.bib
+csl: ../template/oikos.csl
+bibliography: ../template/ref.bib
 ---
@@
 
-\clearpage
+More details can be found at [here](https://bookdown.org/yihui/bookdown/).
 

### 2017-09-25 Doc/ms.Rmd
line space can be set in the yaml

@@
 fontsize: 12pt
+linestretch: 1.5
 link-citations: yes

### 2017-11-16 Doc/respond_to_reviewer.Rmd
add responses to reviwers template

---
title: "Response to reviewers"
author: "Daijiang Li"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    css: ../template/respond_to_reviewer.css
    keep_md: no
    theme: readable
    toc: yes
  pdf_document:
    highlight: zenburn
    keep_tex: no
    template: ../template/respond_to_reviewer.tex
    toc: no
    toc_depth: 3
    latex_engine: xelatex
  word_document: default
---

```{r knitr_options, echo=FALSE}
library(knitr)
opts_chunk$set(fig.align='center', cache=TRUE, warning = FALSE, message = FALSE)
# load(".RData")
options(digits = 3, width = 88)

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.css'
# change directory accordingly
if(!file.exists(tpl_1f <- '../template/respond_to_reviewer.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- '../template/respond_to_reviewer.css')) download.file(tpl_2, tpl_2f)
```

Dear Editors,

Thank you for your help with our manuscript. The constructive comments from reviewers and Editors have greatly improved it.

Sincerely,

Daijiang Li

>09-Nov-2017

>Dear Dr. Li

>We have now completed the review process on your manuscript ....

>You will find the reports of the referees (if any), and the comments of the handling editor, ...

>I invite you to

>Thank you again for submitting to ....

>Yours sincerely

>Editor-in-chief

----------------

### EDITOR-IN-CHIEF'S COMMENTS TO AUTHORS

--

----------------

### EDITOR'S COMMENTS TO AUTHORS

>Editor:   
>Comments to the Author:
>Dear authors

>Thanks for your resubmission, ...

>Best wishes,
>Editor...

We have added qualifiers in these subsections as suggested.

>L299 change ‘reveal’ to ‘suggest’ or ‘imply’ or similar.

Changed 'reveal' to "suggest."

### REVIEWER COMMENTS TO AUTHORS

---------------

>If there are no comments above, the reviewer may have chosen to upload a file. Please check ScholarOne Manuscripts for any attached files, which may be found at the end of the decision letter in your author centre under 'Manuscripts with decisions'.

### 2017-11-16 Doc/ms.Rmd
add responses to reviwers template

--- 2017-04-26 Doc/ms.Rmd
@@
 fontsize: 12pt
+linestretch: 1.5
 link-citations: yes
-csl: ../template/oikos.csl
+csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
 bibliography: ../template/ref.bib
@@
 options(digits = 3, width = 88)
+
+# download template files if not available
+tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/preamble.tex'
+tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/doc_prefix.tex'
+# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
+# change directory accordingly
+if(!file.exists(tpl_1f <- '../template/preamble.tex')) download.file(tpl_1, tpl_1f)
+if(!file.exists(tpl_2f <- '../template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
 ```

### 2020-06-30 Doc/ms.Rmd
update ms.rmd and preamble.tex

--- 2017-04-26 Doc/ms.Rmd
@@
     keep_tex: yes
-    latex_engine: pdflatex
+    latex_engine: xelatex
     number_sections: no
@@
 fontsize: 12pt
+linestretch: 1.5
 link-citations: yes
-csl: ../template/oikos.csl
+csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
 bibliography: ../template/ref.bib
+always_allow_html: yes
+links-as-notes: true
 ---
@@
 opts_knit$set(root.dir = normalizePath("../")) 
-opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
-options(digits = 3, width = 88)
+opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
+  message = TRUE, echo = FALSE)
+options(digits = 3, width = 88, knitr.graphics.auto_pdf = TRUE,
+        knitr.kable.NA = '')
+
+# download template files if not available
+tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/preamble.tex'
+tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/doc_prefix.tex'
+# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
+# change directory accordingly
+if(!file.exists(tpl_1f <- '../template/preamble.tex')) download.file(tpl_1, tpl_1f)
+if(!file.exists(tpl_2f <- '../template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
+if(knitr::is_latex_output() | knitr::is_html_output()){
+  library(kableExtra)
+} else {
+  options(kableExtra.auto_format = FALSE) # for docx
+}
 ```

### 2021-11-02 Doc/respond_to_reviewer.Rmd
update demo

@@
 output:
+  pdf_document:
+    highlight: zenburn
+    keep_tex: no
+    template: template/respond_to_reviewer.tex
+    toc: yes
+    toc_depth: 3
+    latex_engine: xelatex
   html_document:
-    css: ../template/respond_to_reviewer.css
+    css: template/respond_to_reviewer.css
     keep_md: no
@@
     toc: yes
-  pdf_document:
-    highlight: zenburn
-    keep_tex: no
-    template: ../template/respond_to_reviewer.tex
-    toc: no
-    toc_depth: 3
-    latex_engine: xelatex
   word_document: default
@@
 library(knitr)
-opts_chunk$set(fig.align='center', cache=TRUE, warning = FALSE, message = FALSE)
-# load(".RData")
-options(digits = 3, width = 88)
+# rstudio will set the folder where .Rmd file seats as work directory
+# set it back to the folder where .Rproj seats
+opts_knit$set(root.dir = normalizePath("../")) 
+opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
+  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
+options(digits = 3, width = 88,
+        # use pdf file automatically when compile to pdf
+        knitr.graphics.auto_pdf = TRUE, 
+        knitr.kable.NA = '')
 
 # download template files if not available
-tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.tex'
-tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.css'
+tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/respond_to_reviewer.tex'
+tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/respond_to_reviewer.css'
 # change directory accordingly
-if(!file.exists(tpl_1f <- '../template/respond_to_reviewer.tex')) download.file(tpl_1, tpl_1f)
-if(!file.exists(tpl_2f <- '../template/respond_to_reviewer.css')) download.file(tpl_2, tpl_2f)
+if(!file.exists(tpl_1f <- 'template/respond_to_reviewer.tex')) download.file(tpl_1, tpl_1f)
+if(!file.exists(tpl_2f <- 'template/respond_to_reviewer.css')) download.file(tpl_2, tpl_2f)
+
+if(knitr::is_latex_output() | knitr::is_html_output()){
+  library(kableExtra)
+} else {
+  options(kableExtra.auto_format = FALSE) # for docx
+}
 ```
-
-Dear Editors,
-
-Thank you for your help with our manuscript. The constructive comments from reviewers and Editors have greatly improved it.
-
-Sincerely,
-
-Daijiang Li
 
@@
 
-----------------
-
 ### EDITOR-IN-CHIEF'S COMMENTS TO AUTHORS
 
---
+>xxxxxxxxxx
 
-----------------
+Dear Editors,
+
+Thank you for your help with our manuscript. The constructive comments from reviewers and Editors have greatly improved it.
+
+Sincerely,
+
+Daijiang Li
 
@@
 
----------------
-
 >If there are no comments above, the reviewer may have chosen to upload a file.
 Please check ScholarOne Manuscripts for any attached files, which may be found at the end of the decision letter in your author centre under 'Manuscripts with decisions'.
+
+Thank you and here is our responses.

### 2021-11-02 Doc/ms.Rmd
update demo

--- 2017-09-25 Doc/ms.Rmd
@@
 title: "Your Awesome Title"
-author: "Author One and Author Two"
+author: "Author One^1^* and Author Two^2^"
 date: '`r format(Sys.time())`'
@@
     includes:
-      before_body: ../template/doc_prefix.tex
-      in_header: ../template/preamble.tex
+      before_body: template/doc_prefix.tex
+      in_header: template/preamble.tex
     keep_tex: yes
-    latex_engine: pdflatex
+    latex_engine: xelatex
     number_sections: no
@@
     toc: yes
-  bookdown::word_document2: null
+  bookdown::word_document2:
+    toc: no
+    reference_docx: template/nature_style.docx
+    number_sections: no
 fontsize: 12pt
@@
 link-citations: yes
-csl: ../template/oikos.csl
-bibliography: ../template/ref.bib
+csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
+bibliography: ref.bib
+always_allow_html: yes
+links-as-notes: true
+notes-after-punctuation: false
 ---
@@
 opts_knit$set(root.dir = normalizePath("../")) 
-opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
-options(digits = 3, width = 88)
+opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
+  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
+options(digits = 3, width = 88,
+        # use pdf file automatically when compile to pdf
+        knitr.graphics.auto_pdf = TRUE, 
+        knitr.kable.NA = '')
+
+# download template files if not available
+tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/preamble.tex'
+tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/doc_prefix.tex'
+tpl_3 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/nature_style.docx'
+# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
+# change directory accordingly
+if(!file.exists(tpl_1f <- 'template/preamble.tex')) download.file(tpl_1, tpl_1f)
+if(!file.exists(tpl_2f <- 'template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
+if(!file.exists(tpl_3f <- 'template/nature_style.docx')) download.file(tpl_3, tpl_3f)
+
+if(knitr::is_latex_output() | knitr::is_html_output()){
+  library(kableExtra)
+} else {
+  options(kableExtra.auto_format = FALSE) # for docx
+}
 ```
+
+\footnotesize
+
+^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
+^2^Center for Computation & Technology, Louisiana State University, Baton Rouge, LA, USA
+
+\* **Corresponding author**, email: daijianglee@gmail.com; 125 Life Science Building, Baton Rouge, LA 70803
+
+\normalsize
 
@@
 
+(ref:captionTable1) **Model coefficients of leaf senescence based on in situ data**. No space at the end of this line!!
+
 ```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
 source("R/rcode.R")
-knitr::kable(sprich, booktabs = T, caption = "Caption here.")
+# linesep = c('', '', '', '', '', '\\addlinespace') 
+# can be used within kable to specify linespace
+knitr::kable(sprich, booktabs = T, caption = '(ref:captionTable1)')  %>%
+ kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "condensed", "hover"), 
+                           latex_options = c("striped", "HOLD_position")) # , "scale_down"
 ```
@@
 
-```{r figName, fig.width=7, fig.asp=1, fig.cap="Your caption here."}
+(ref:captionFig1) **No - or _ in the caption ref.** No space at the end of this line!
+
+```{r figName, fig.width=7, fig.asp=1, fig.cap="(ref:captionFig1)"}
 ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
   geom_point() + geom_smooth(method = "lm") +
-  facet_wrap(~envi, scales = "free_x") + theme_bw()
+  facet_wrap(~envi, scales = "free_x") + 
+  theme_bw()
 ```
@@
 Or if you already have the figure:
+
 And cite it as Figure \@ref(fig:fig2).
 
-```{r fig2, out.width='70%', fig.cap="Caption here."}
+(ref:captionFig2) **No - or _ in the caption ref.** No space at the end of this line!
+
+```{r fig2, out.width='70%', fig.cap="(ref:captionFig2)"}
 knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
@@
 # References
+
+<div id="refs"></div>
+
+\clearpage
+
+\setcounter{page}{0}
+\pagenumbering{arabic}
+\setcounter{page}{1}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\renewcommand {\thetable}{S\arabic{table}}
+\renewcommand {\thefigure}{S\arabic{figure}}
+
+# Supporting Information
+
+## Figures
+
+(ref:captionFigS1) **No - or _ in the caption ref.** No space at the end of this line!
+
+```{r figS1, out.width='70%', fig.cap="(ref:captionFigS1)"}
+knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
+```

### 2021-11-02 Doc/ms.tex
relocate template files
update demo

@@
-\documentclass[12pt,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
 \usepackage{lmodern}
+\usepackage{setspace}
 \usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Your Awesome Title},
+  pdfauthor={Author One1* and Author Two2},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Your Awesome Title},
-            pdfauthor={Author One and Author Two},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
 \usepackage{longtable,booktabs}
-\usepackage{graphicx,grffile}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+% Make links footnotes instead of hotlinks:
+\DeclareRobustCommand{\href}[2]{#2\footnote{\url{#1}}}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-  \title{Your Awesome Title}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \author{Author One and Author Two}
-  \preauthor{\centering\large\emph}
-  \postauthor{\par}
-  \predate{\centering\large\emph}
-  \postdate{\par}
-  \date{2017-02-28 12:56:45}
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{geometry}
@@
 
-\usepackage[utf8]{inputenc}
+% \usepackage[T1]{fontenc}
+% \usepackage[utf8]{inputenc}
+% \usepackage{textgreek}
+\usepackage{babel}
+% % \usepackage{microtype}
+% % \usepackage{amsmath}
+\usepackage[osf]{libertine}
+\usepackage{libertinust1math}
+\usepackage{inconsolata}
+
+\usepackage{longtable}
 
@@
 \usepackage{setspace}
-\doublespacing
+% \doublespacing
 
@@
 \usepackage{lineno}
-\linenumbers
+% \linenumbers
 
-\renewcommand{\rmdefault}{cmr}
+\usepackage{flafter}
+\usepackage{float}
 
-% flush left while keep identation
-\makeatletter
-\newcommand\iraggedright{%
-  \let\\\@centercr\@rightskip\@flushglue \rightskip\@rightskip
-  \leftskip\z@skip}
-\makeatother
+% \renewcommand{\rmdefault}{cmr}
+
+\usepackage[document]{ragged2e}
+
+% % flush left while keep identation
+% \makeatletter
+% \newcommand\iraggedright{%
+%   \let\\\@centercr\@rightskip\@flushglue \rightskip\@rightskip
+%   \leftskip\z@skip}
+% \makeatother
+% \raggedright
+
+% make pdf as default figure format
+\DeclareGraphicsExtensions{.pdf,.png, %
+    .jpg,.mps,.jpeg,.jbig2,.jb2,.JPG,.JPEG,.JBIG2,.JB2}
+
+% \DeclareUnicodeCharacter{3B1}{\ensuremath{\alpha}}
+% \DeclareUnicodeCharacter{3B2}{\ensuremath{\beta}}
+% \DeclareUnicodeCharacter{0394}{$\Delta$}
+
+\usepackage[labelsep=period]{caption}
+\captionsetup{labelfont=bf}
+% \usepackage{caption}
+% \DeclareCaptionLabelSeparator{vline}{ \textbf{|} }
+% \captionsetup{labelsep=vline, labelfont = {bf}}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
+
+\title{Your Awesome Title}
+\author{Author One\textsuperscript{1}* and Author Two\textsuperscript{2}}
+\date{2021-11-02 15:56:55}
 
@@
 % align only at left, not at right.
-\iraggedright
+\renewcommand{\figurename}{{\textbf{Figure}}}
+\renewcommand{\tablename}{{\textbf{Table}}}
+% \iraggedright
+
+\setstretch{1.5}
+\footnotesize
+
+\textsuperscript{1}Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA\\
+\textsuperscript{2}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA
+
+* \textbf{Corresponding author}, email: \href{mailto:daijianglee@gmail.com}{\nolinkurl{daijianglee@gmail.com}}; 125 Life Science Building, Baton Rouge, LA 70803
+
+\normalsize
 
@@
 
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Here is your introduction. It should describe clearly the rationale for
-the study being done and the previous work related with the study. It
-should also tell readers about your specific hypothese/questions being
-addressed. Citations will be like this (Adair et al.
-\protect\hyperlink{ref-adair_single-pool_2010}{2010}), or (e.g., Clark
-and Tilman \protect\hyperlink{ref-clark_loss_2008}{2008}), or (Eriksson
-and Ehrlén \protect\hyperlink{ref-eriksson_seed_1993}{1993}, Williamson
-et al. \protect\hyperlink{ref-williamson_dissolved_1999}{1999})
+Here is your introduction.
+It should describe clearly the rationale for the study being done and the previous work related with the study.
+It should also tell readers about your specific hypothese/questions being addressed.
+Citations will be like this (Adair et al.
+\protect\hyperlink{ref-adair_single-pool_2010}{2010}), or (e.g., Clark and Tilman \protect\hyperlink{ref-clark_loss_2008}{2008}), or (Eriksson and Ehrlén \protect\hyperlink{ref-eriksson_seed_1993}{1993}, Williamson et al.
+\protect\hyperlink{ref-williamson_dissolved_1999}{1999})
 
@@
 
-\section{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-Here is the method section. You can include equations easily. For inline
-equations, use \(\text{var}(X) = p(1-p)\). For display equation, use
+Here is the method section. You can include equations easily. For inline equations, use \(\text{var}(X) = p(1-p)\). For display equation, use
 
@@
 
-\subsection{Results}\label{results}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-\paragraph{Tables}\label{tables}
+\hypertarget{tables}{%
+\paragraph{Tables}\label{tables}}
 
-Insert tables by \texttt{kable} in knitr package in R. Then
-cross-reference it back with: see Table \ref{tab:tableName}.
+Insert tables by \texttt{kable} in knitr package in R. Then cross-reference it back with: see Table \ref{tab:tableName}.
 
-\begin{table}
+\begin{table}[H]
 
-\caption{\label{tab:tableName}Caption here.}
+\caption{\label{tab:tableName}\textbf{Model coefficients of leaf senescence based on in situ data}. No space at the end of this line!!}
 \centering
@@
 \midrule
-3294 & 31\\
+\cellcolor{gray!6}{3294} & \cellcolor{gray!6}{31}\\
 3297 & 28\\
-3299 & 26\\
+\cellcolor{gray!6}{3299} & \cellcolor{gray!6}{26}\\
 3330 & 27\\
@@
 
-\paragraph{\texorpdfstring{Insert tables by \texttt{xtable} package in
-R}{Insert tables by xtable package in R}}\label{insert-tables-by-xtable-package-in-r}
+\hypertarget{insert-tables-by-xtable-package-in-r}{%
+\paragraph{\texorpdfstring{Insert tables by \texttt{xtable} package in R}{Insert tables by xtable package in R}}\label{insert-tables-by-xtable-package-in-r}}
 
@@
 
-\paragraph{Insert tables by hand}\label{insert-tables-by-hand}
+\hypertarget{insert-tables-by-hand}{%
+\paragraph{Insert tables by hand}\label{insert-tables-by-hand}}
 
@@
 
-\paragraph{Figures}\label{figures}
+\hypertarget{figures}{%
+\paragraph{Figures}\label{figures}}
 
-Insert figure by code chunk. And cross-ref it back as Figure
-\ref{fig:figName}.
+Insert figure by code chunk. And cross-ref it back as Figure \ref{fig:figName}.
 
-\begin{figure}
+\begin{verbatim}
+## `geom_smooth()` using formula 'y ~ x'
+\end{verbatim}
+
+\begin{figure}[H]
 
@@
 
-\caption{Your caption here.}\label{fig:figName}
+\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:figName}
 \end{figure}
 
-Or if you already have the figure: And cite it as Figure \ref{fig:fig2}.
+Or if you already have the figure:
 
-\begin{figure}
+And cite it as Figure \ref{fig:fig2}.
 
-{\centering \includegraphics[width=0.7\linewidth]{/Users/dli/Github/workflow_demo/Figs/plot}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.7\linewidth,]{/Users/dli/github/workflow_demo/Figs/plot}
 
@@
 
-\caption{Caption here.}\label{fig:fig2}
+\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:fig2}
 \end{figure}
+
+More details can be found at \href{https://bookdown.org/yihui/bookdown/}{here}.
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{cslreferences}
+\leavevmode\hypertarget{ref-adair_single-pool_2010}{}%
+Adair, E. C., S. E. Hobbie, and R. K. Hobbie. 2010. Single-pool exponential decomposition models: Potential pitfalls in their use in ecological studies. Ecology 91:1225--1236.
+
+\leavevmode\hypertarget{ref-clark_loss_2008}{}%
+Clark, C. M., and D. Tilman. 2008. Loss of plant species after chronic low-level nitrogen deposition to prairie grasslands. Nature 451:712--715.
+
+\leavevmode\hypertarget{ref-eriksson_seed_1993}{}%
+Eriksson, O., and J. Ehrlén. 1993. Seed and microsite limitation of recruitment in plant populations. Oecologia 92:361--366.
+
+\leavevmode\hypertarget{ref-williamson_dissolved_1999}{}%
+Williamson, C.
+E., D.
+P.
+Morris, M.
+L.
+Pace, and O.
+G.
+Olson.
+1999.
+Dissolved organic carbon and nutrients as regulators of lake ecosystems: Resurrection of a more integrated paradigm.
+Limnology and Oceanography 44:795--803.
+\end{cslreferences}
 
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
+\setcounter{page}{0}
+\pagenumbering{arabic}
+\setcounter{page}{1}
 
-\hypertarget{refs}{}
-\hypertarget{ref-adair_single-pool_2010}{}
-Adair, E. C. et al. 2010. Single-pool exponential decomposition models:
-Potential pitfalls in their use in ecological studies. - Ecology 91:
-1225--1236.
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\renewcommand {\thetable}{S\arabic{table}}
+\renewcommand {\thefigure}{S\arabic{figure}}
 
-\hypertarget{ref-clark_loss_2008}{}
-Clark, C. M. and Tilman, D. 2008. Loss of plant species after chronic
-low-level nitrogen deposition to prairie grasslands. - Nature 451:
-712--715.
+\hypertarget{supporting-information}{%
+\section{Supporting Information}\label{supporting-information}}
 
-\hypertarget{ref-eriksson_seed_1993}{}
-Eriksson, O. and Ehrlén, J. 1993. Seed and microsite limitation of
-recruitment in plant populations. - Oecologia 92: 361--366.
+\hypertarget{figures-1}{%
+\subsection{Figures}\label{figures-1}}
 
-\hypertarget{ref-williamson_dissolved_1999}{}
-Williamson, C. E. et al. 1999. Dissolved organic carbon and nutrients as
-regulators of lake ecosystems: Resurrection of a more integrated
-paradigm. - Limnology and Oceanography 44: 795--803.
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.7\linewidth,]{/Users/dli/github/workflow_demo/Figs/plot}
+
+}
+
+\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:figS1}
+\end{figure}
 

### 2021-11-02 R/rcode.R

@@ -1,28 +1,25 @@
 # packages needed
-library(stringr)
 library(plyr)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
+library(tidyverse)
 
 # read data into R
-under2012=read.csv("Data/Raw_data/under2012.csv",stringsAsFactors=F)
+under2012 = read.csv("Data/Raw_data/under2012.csv")
 envi = read.csv("Data/Raw_data/envi.csv")
 
-# data clean: you should clean your data with scripts instead of doing it 
-# in Excel. By using scripts, you recorded all of your history about data 
+# data clean: you should clean your data with scripts instead of doing it
+# in Excel. By using scripts, you recorded all of your history about data
 # clean. You should also make comments about why you changed your data.
 # names(under2012)
-under2012$Genera=str_trim(under2012$Genera) #remove spaces before and after sp.names.
-under2012$species=str_trim(under2012$species) 
-under2012[under2012$species=="sp",]$species="spp" # change sp to spp
-under2012$sp=paste(under2012$Genera,under2012$species) # combine genus and sp
+under2012$Genera = str_trim(under2012$Genera) #remove spaces before and after sp.names.
+under2012$species = str_trim(under2012$species)
+under2012[under2012$species == "sp", ]$species = "spp" # change sp to spp
+under2012$sp = paste(under2012$Genera, under2012$species) # combine genus and sp
 # sort(unique(under2012$sp))
 
 ## correct sp names' typo and errors
-under2012[under2012$sp=="Accer rubrum",]$sp="Acer rubrum"
-under2012[under2012$sp=="Acrtostaphylos uva-ursi",]$sp="Arctostaphylos uva-ursi"
-under2012[under2012$sp=="Carex pennsylvanica",]$sp="Carex pensylvanica"
+under2012[under2012$sp == "Accer rubrum", ]$sp = "Acer rubrum"
+under2012[under2012$sp == "Acrtostaphylos uva-ursi", ]$sp = "Arctostaphylos uva-ursi"
+under2012[under2012$sp == "Carex pennsylvanica", ]$sp = "Carex pensylvanica"
 
 # remove columns we do not need
 under2012 = under2012[c("Plot", "Transect", "Quadrat", "sp", "Count")]
@@ -35,8 +32,11 @@ sprich = ddply(under2012, .(Plot), summarize, sprich = length(unique(sp)))
[…]
